RJObject Manual

### 2015-12-07 Documents/manual.tex
Using SineWaves example

RJObject provides sensible default moves, drastically reducing the amount of
work required to write the model class.

>>>>

RJObject provides sensible default moves, drastically reducing the amount of
work required to write the model class. In the Examples/SineWaves directory,
the model is specified in the MyModel class. If you open MyModel.h you'll
notice the MyModel class doesn't have very many data members:

\begin{framed}
\begin{verbatim}
class MyModel:public DNest3::Model
{
    private:
        RJObject<MyDistribution> objects;
        double sigma;

        std::vector<long double> mu;
}
\end{verbatim}
\end{framed}

The variable {\tt objects}, of type {\tt RJObject<MyDistribution>}, represents
$\left\{N, \{A_i, T_i, \phi_i\}_{i=1}^N\right\}$. The only other parameter
is the noise standard deviation $\sigma$. The vector of long doubles is
the ``mock signal'' used in the likelihood function.
